Evaluation of performances

### 2020-02-24 analysis/eval-performance.Rmd
add prefixes to plots and tables

# load drake objects
loadd(
  bm_aggregated_new
)
library("xtable")
library("flextable")
library("ggbeeswarm")
library("ggsci")
library("ggrepel")
library("ggpubr")
```

```{r}
df_perf <- getBMRPerformances(bm_aggregated_new, as.df = T) %>%
  mutate(task.id = recode_factor(task.id,
    `hr` = "HR",
    `vi` = "VI",
    `nri` = "NRI",
    `nri_vi` = "NRI_VI",
    `hr_nri` = "HR-NRI",
    `hr_vi` = "HR-VI",
    `hr_nri_vi` = "HR-NRI-VI",
  )) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " MBO "
  )
```

@@

## (Table) All leaner/filter/task combinations ordered by performance.

@@

## (Table) Best learner/filter/task combination

@@

saveRDS(table2, "docs/00-manuscripts/ieee/presentation/table-best-learner-per-task.rda")

@@

## (Plot) Best learner/filter combs for all tasks

@@

## (Plot) Best filter combination of each learner vs. no filter per task vs. Borda

@@

## (Plot) Best filter combination of each learner vs. Borda filter

@@

## (Plot) Performances of all filter methods

@@

## (Plot) Scatterplots of filter methods vs. no filter for each learner and task

@@

## (Plot) Scatterplots of filter methods vs. Borda for each learner and task

@@

results_aggr2 %>%
  ggplot(aes(x = perf, y = fct_reorder(learner_group, -perf))) +
  geom_beeswarm(
    data = results_aggr2[results_aggr2$filter != "Borda", ],
    shape = 3, size = 1.1, aes(color = "Filter"),
    groupOnX = FALSE
  ) +
  geom_point(
    data = results_aggr2[results_aggr2$filter == "Borda", ],
    shape = 19, size = 2, aes(color = "Borda Filter")
  ) +
  facet_wrap(~task.id) +
  scale_color_manual(guide = guide_legend(override.aes = list(shape = c(19, 3))),
                     values = c("Filter" = "#BC8C29FF",
                     "Borda Filter" = "#0072B5FF")) +
  labs(x = "RMSE", y = "Task", colour = NULL) +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(27, 51)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
  )
```

>>>>

# load drake objects
loadd(
  bm_aggregated_new_buffer2
)
library("xtable")
library("flextable")
library("ggbeeswarm")
library("ggsci")
library("ggrepel")
library("ggpubr")
```

```{r}
df_perf <- getBMRPerformances(bm_aggregated_new_buffer2, as.df = T) %>%
  mutate(task.id = recode_factor(task.id,
    `hr_buffer2` = "HR",
    `vi_buffer2` = "VI",
    `nri_buffer2` = "NRI",
    `nri_vi_buffer2` = "NRI_VI",
    `hr_nri_buffer2` = "HR-NRI",
    `hr_vi_buffer2` = "HR-VI",
    `hr_nri_vi_buffer2` = "HR-NRI-VI",
  )) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " MBO "
  )
```

@@

## (Table) T1 All leaner/filter/task combinations ordered by performance.

@@

## (Table) T2 Best learner/filter/task combination

@@

saveRDS(table2, "docs/00-manuscripts/presentation/table-best-learner-per-task.rda")

@@

## (Plot) P1 Best learner/filter combs for all tasks

@@

## (Plot) P2 Best filter combination of each learner vs. no filter per task vs. Borda

@@

## (Plot) P3 Best filter combination of each learner vs. Borda filter

@@

## (Plot) P4 Performances of all filter methods

@@

## (Plot) P5 Scatterplots of filter methods vs. no filter for each learner and task

@@

## (Plot) P6 Scatterplots of filter methods vs. Borda for each learner and task

@@

results_aggr2 %>%
  ggplot(aes(x = perf, y = fct_reorder(learner_group, -perf))) +
  geom_beeswarm(
    data = results_aggr2[results_aggr2$filter != "Borda", ],
    shape = 3, size = 1.1, aes(color = "Filter"),
    groupOnX = FALSE
  ) +
  geom_point(
    data = results_aggr2[results_aggr2$filter == "Borda", ],
    shape = 19, size = 2, aes(color = "Borda Filter")
  ) +
  facet_wrap(~task.id) +
  scale_color_manual(
    guide = guide_legend(override.aes = list(shape = c(19, 3))),
    values = c(
      "Filter" = "#BC3C29FF",
      "Borda Filter" = "#0072B5FF"
    )
  ) +
  labs(x = "RMSE", y = "Task", colour = NULL) +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(27, 51)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
  )
```

```{r echo = FALSE}
copy_figures()
```
